---
title: "cloudbrewr-dotdotdot-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cloudbrewr-dotdotdot-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cloudbrewr)
library(dplyr)
```

## What is Dot Dot Dot function in R?
It means that the function is designed to take any number of named or unnamed arguments. Just like Python `*kwargs` parameter

## How do we use it in this library?
Say you are getting an object from S3 and you realize that you might need an extra parameter in your `s3 get object`. 

`aws_s3_get_object` is built with `...`, and you can find extra parameter that you can use from the [Paws official API Docs](https://paws-r.github.io/docs/s3/get_object.html). 

So, you are able to modify your S3 get with some specific versioning needs by:
```{r}
aws_s3_get_object(
  bucket = 'databrew.org',
  key = 'kwale/raw-form/reconbhousehold/reconbhousehold.csv',
  VersionId = 'NaFvmYr2_E3x57xPBMmyvaK6Ar3fi1k7' # represents the 3 dots
) %>% head(5)
```






