---
title: "CloudBrewR S3 Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CloudBrewR S3 Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cloudbrewr)
library(data.table)
library(dplyr)
```

### Log in to AWS @DataBrew

Let's take
```{r eval = FALSE}
aws_login(
    role_name = 'cloudbrewr-aws-role',
    profile_name = 'dbrew-cloudbrewr-aws-role')
```

After running login, depending in your session there will be two login types. 

- Interactive Session (RStudio, RSession): Function will trigger SSO login through our [DataBrew AWS Portal](https://databrewllc.awsapps.com/start#/)

- Bash / EC2 / Containers: Function will prompt user to export access keys directly from our  
[DataBrew AWS Portal](https://databrewllc.awsapps.com/start#/). This is more representative of production data pipeline that uses IAM Roles

### Get an Object from S3
```{r}
aws_s3_get_object(
  bucket = 'databrew.org', 
  key = 'bohemiatesting-ke/raw-form/reconhh/reconhh.csv')

object <- aws_s3_get_object(
  bucket = 'databrew.org', 
  key = 'bohemiatesting-ke/raw-form/reconhh/reconhh.csv')
```

Running the object getter will give user with the metadata of the object, starting from item size `content_length`, `version_id`, and other s3-related information. To read .csv file locally run:

```{r}
data <- fread(object$file_path) %>% 
  dplyr::select(SubmissionDate) %>%
  head(5)
data
```

By default, data is save to `~/.cloudbrew_cache`, to change to existing directory use `output_dir` parameter:

```{r}
object <- aws_s3_get_object(
  bucket = 'databrew.org', 
  key = 'bohemiatesting-ke/raw-form/reconhh/reconhh.csv',
  output_dir = 'data')
```

### Storing an Object to S3 bucket (@Internal Use)

Say you want to save the output again to S3, this is the procedure to store the data:
```{r}
tempfile <- tempfile(fileext = ".csv")
data %>% fwrite(tempfile)
aws_s3_store(
  filename = tempfile, 
  bucket = 'databrew.org', 
  key = 'bohemiatesting-ke/test.csv',
  namespace_bucket = TRUE)
```


